Containers and R---the Rockerverse and beyond

### 2020-01-13 manuscript.Rmd
add link for dockr

- [`dockerfiler`](https://github.com/ColinFay/dockerfiler/)
- [`containerit`](https://github.com/o2r-project/containerit/)
- [`dockr`](https://github.com/smaakage85/dockr)
- [`dockertest`](https://github.com/traitecoevo/dockertest/)
- [`renv` with Docker](https://rstudio.github.io/renv/articles/docker.html)

>>>>

- [`dockerfiler`](https://github.com/ColinFay/dockerfiler/)
- [`containerit`](https://github.com/o2r-project/containerit/)
- [`dockr`](https://github.com/smaakage85/dockr), see also http://smaakage85.netlify.com/2019/12/21/dockr-easy-containerization-for-r/
- [`dockertest`](https://github.com/traitecoevo/dockertest/)
- [`renv` with Docker](https://rstudio.github.io/renv/articles/docker.html)
